---
title: "Comparing the effect of Z variability on model efficacy"
author: "Charles Hinchliffe"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


The .rmd demonstartes the effect of variation in s0 on classic catch-curve methods, our continous catch-curve, and our R/Z age-distribution model. To 'age' the data we take the ages that are produced when a population is simulated using simulate_catch_data().


# Load require packages and functions

```{r}
library(rstan)
library(tidyverse)
library(rstan)
library(dplyr)
library(ggplot2)
library(see)
library(FSA)
library(fishmethods)
library(pracma)
library(bayesplot)
library(bayesboot)
library(see)
library(IDPmisc)

#agesurv funtion from 'fishmethods' with decimal rounding removed
source("R/agesurv_no_rounding.R")

#Data generation and manipulation functions
source("R/generate_sample.R")
source("R/trim_data_to_mode.R")
source("R/create_bins.R")

#For re-aging
source("R/real_aged_method.R")

#prapre data for stan model
source("R/data_for_stan_age.R")

#Plotting functions
source("R/plot_age_dist.R")
source("R/plot_size_dist.R")
source("R/element_textbox.R")
```


# Example
```{r}
#for plotting
pars <- list(R = 500,
             s0_av = 3,
             log10s0_sd = 0,
             g_av = 0.21,
             log10g_sd = 0,
             z_av = 0.25, 
             log10z_sd = 0.0,
             bin_width_age = 1,
             bin_width_size = 0.1)

#simulate population
data <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.0)

data2 <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.1)

data3 <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.3)


```

# Plot simulated population
```{r}

plot_size_dist(data,pars)

plot_size_dist(data2,pars)

plot_size_dist(data3,pars)

```


# Read in stan models
```{r, eval = FALSE}
#age distribution model estimates R and Z
ret_age <- stan_model(file="stan/mortality_age.stan")

```



# Select log10z_sd variability 
```{r}
variance <- c(0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              
              
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              
              
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              
              
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              
              
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              
              
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              
              
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1
              
              ) #700 0.1


normalised_data <- as.data.frame(variance)

```


# Run models
```{r, eval = FALSE}
tryCatch(
for(i in seq_len(nrow(normalised_data))){

#generate data  
data <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = variance[i]) 


#create age and size bins
data <- create_bins(data,
                    bin_width_age = 1,
                    bin_width_size = 0.1)



###select subset of individuals for 'ageing' and apply linear model or ALK. Eg: simulating age/length(or weight) measurements made in lab from subset of individuals across all ages/sizes 

data <- real_aged_data(data = data)

#get sample size
normalised_data$sample_size[i] <- nrow(data)


#Sort ages into age bins, 1 day width
bin_width <- 1

cat_data <- lencat(~estimated_age, data = data, startcat = 0, w = bin_width, vname = "ageCat") ## uses agecat data, bins set at 1 day

## mode function for fully recruited age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


# Calculate the mode using the user function.
recruit_age <- getmode(cat_data$ageCat)
recruit_age

 
#Catch-curve method (Linear regression)
catch_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "lr") ##

normalised_data$catch_curve[i] <- as.numeric(catch_curve$`results`[3]) # extract z

#truncated catch-curve (weighted Linear regression)
trunc_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "wlr") ##

normalised_data$weighted_catch_curve[i] <- as.numeric(trunc_curve$`results`[3])# extract z



#Chapman-robson method
CRZ <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "crcb") 

normalised_data$Chapman_Robson[i] <- as.numeric(CRZ$`results`[3]) # extract z


#select data sample from stan known g model
data2 <- data_for_stan_age(data = data, bin_width_age = 1)

##sample from stan model
fit_age <- sampling(ret_age, data = data2, iter = 999, chains = 3)

normalised_data$stan_age[i] <- mean(rstan::extract(fit_age, pars="Z")[["Z"]])



}, error=function(e) e
)

saveRDS(normalised_data, "output/all_ages_z.rds")
```

# Read in output
```{r}
normalised_data <- readRDS("output/all_ages_z.rds")

head(normalised_data)
```







# Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")

normalised_data_long <- gather_(normalised_data, keycol, valuecol, gathercols)

head(normalised_data_long)
tail(normalised_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(normalised_data_long, aes(variance, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```
 
 
Plot var groups seperately  

variance <- c(0,0,0,0,0,0,0,0,0,0,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1)
```{r,eval=FALSE}
#Z_var = 0.00
var0 <- subset(normalised_data_long, variance == 0)

p5 <- ggplot(var0, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p5

##Z_var = 0.01
var0.01 <- subset(normalised_data_long, variance == 0.01)

p6 <- ggplot(var0.01, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0.01") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p6

#Z_var = 0.025
var0.02 <- subset(normalised_data_long, variance == 0.02)


p7 <- ggplot(var0.02, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0.02") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p7

#var = 0.03
var0.03 <- subset(normalised_data_long, variance == 0.03)


p8 <- ggplot(var0.03, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0.03") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p8

#var = 0.05
var0.05<- subset(normalised_data_long, variance == 0.05)


p9 <- ggplot(var0.05, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0.05") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p9
#var = 0.1
var0.1 <- subset(normalised_data_long, variance == 0.1)


p10 <- ggplot(var0.1, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10z_sd = 0.1") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p10
```


# Facet plot

Device size 6 x 13inch
```{r}

data <- normalised_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")))
  
data

fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(Z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "z variance")#labs(title = expression('Variability around'~ bar(Z)))
 

fac_plot

all_age_z_var_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "z variance") #+  
  #theme(plot.title = element_textbox(hjust = 0.5, margin = margin(t = 5, b = 5)) #labs(title = expression('*Variability around*'~ bar(Z)))
 

all_age_z_var_fac_plot
```


# Extract data for summary table
## catch curve
```{r}
#catch curve
CC5 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.005) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.01) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.02) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.03) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.05) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.1) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```
## weighted catch curve
```{r}
#catch curve
wCC5 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.005) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.01) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.02) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.03) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.05) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.1) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.005) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.01) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.02) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.03) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.05) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.1) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan age
```{r}
#Chapman robson
SA5 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0) %>%
  select(stan_age) 

mean(NaRV.omit(SA5$stan_age))
sd(NaRV.omit(SA5$stan_age))

#
SA10 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.005) %>%
  select(stan_age) 

mean(NaRV.omit(SA10$stan_age))
sd(NaRV.omit(SA10$stan_age))

#
SA20 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.01) %>%
  select(stan_age) 


mean(NaRV.omit(SA20$stan_age))
sd(NaRV.omit(SA20$stan_age))

#
SA50 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.02) %>%
  select(stan_age) 


mean(NaRV.omit(SA50$stan_age))
sd(NaRV.omit(SA50$stan_age))

#
SA100 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.03) %>%
  select(stan_age) 


mean(NaRV.omit(SA100$stan_age))
sd(NaRV.omit(SA100$stan_age))

#
SA500 <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.05) %>%
  select(stan_age) 


mean(NaRV.omit(SA500$stan_age))
sd(NaRV.omit(SA500$stan_age))

#
SA <- output_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.1) %>%
  select(stan_age) 


mean(NaRV.omit(SA$stan_age))
sd(NaRV.omit(SA$stan_age))
```


# Normalised results
## Normalise data around mean z 0.25

```{r}
normalised_data <- normalised_data

normalised_data$catch_curve <- ((normalised_data$catch_curve/0.25)*100)-100


normalised_data$weighted_catch_curve <- ((normalised_data$weighted_catch_curve/0.25)*100)-100


normalised_data$Chapman_Robson <- ((normalised_data$Chapman_Robson/0.25)*100)-100


normalised_data$stan_age <- ((normalised_data$stan_age/0.25)*100)-100

head(normalised_data)
```



## Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")

normal_data_long <- gather_(normalised_data, keycol, valuecol, gathercols)

head(normal_data_long)
tail(normal_data_long)
```


## Facet plot

Device size 6 x 13inch
```{r}

data <- normal_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")))
  
data

normal_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(Z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "z variance")#labs(title = expression('Variability around'~ bar(Z)))
 

fac_plot

normal_all_age_z_var_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "z variance") #+  
  #theme(plot.title = element_textbox(hjust = 0.5, margin = margin(t = 5, b = 5)) #labs(title = expression('*Variability around*'~ bar(Z)))
 

normal_all_age_z_var_fac_plot
```

# Extract normalised data for summary table
## catch curve
```{r}
#catch curve
CC5 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.005) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.01) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.02) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.03) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.05) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.1) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```
## weighted catch curve
```{r}
#catch curve
wCC5 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.005) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.01) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.02) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.03) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.05) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.1) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.005) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.01) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.02) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.03) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.05) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.1) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan age
```{r}
#Chapman robson
SA5 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0) %>%
  select(stan_age) 

mean(NaRV.omit(SA5$stan_age))
sd(NaRV.omit(SA5$stan_age))

#
SA10 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.005) %>%
  select(stan_age) 

mean(NaRV.omit(SA10$stan_age))
sd(NaRV.omit(SA10$stan_age))

#
SA20 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.01) %>%
  select(stan_age) 


mean(NaRV.omit(SA20$stan_age))
sd(NaRV.omit(SA20$stan_age))

#
SA50 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.02) %>%
  select(stan_age) 


mean(NaRV.omit(SA50$stan_age))
sd(NaRV.omit(SA50$stan_age))

#
SA100 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.03) %>%
  select(stan_age) 


mean(NaRV.omit(SA100$stan_age))
sd(NaRV.omit(SA100$stan_age))

#
SA500 <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.05) %>%
  select(stan_age) 


mean(NaRV.omit(SA500$stan_age))
sd(NaRV.omit(SA500$stan_age))

#
SA <- normalised_data %>%
 select(variance, stan_age) %>%
  filter(variance == 0.1) %>%
  select(stan_age) 


mean(NaRV.omit(SA$stan_age))
sd(NaRV.omit(SA$stan_age))
```

