---
title: "Comparing the effect differeces between 'true' and literature growth rates have on model efficacy"
author: "Charles Hinchliffe"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


The .rmd demonstartes the effect of having large differences between 'true' and applied literature growth rate on classic catch-curve methods, and our size-distribution model with known G. To age the data a simple linear model is applied to size_sampled using a specificed G from the literature (0.21)

# Load require packages and functions

```{r}
library(rstan)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(FSA)
library(fishmethods)
library(pracma)
library(bayesplot)
library(bayesboot)
library(see)
library(IDPmisc)

#agesurv funtion from 'fishmethods' with decimal rounding removed
source("R/agesurv_no_rounding.R")

#Data generation and manipulation functions
source("R/generate_sample.R")
source("R/trim_data_to_mode.R")
source("R/create_bins.R")

#For re-aging
source("R/age_data_with_literature_growth_rate.R")

#prapre data for stan model
source("R/data_for_stan_size.R")

#Plotting functions
source("R/plot_age_dist.R")
source("R/plot_size_dist.R")
source("R/element_textbox.R")
```


# Read in stan models
```{r, eval = FALSE}
#size distribution model known G
ret_size <- stan_model(file="stan/mortality_size_known_g.stan")
```


# Select g_av percent change
```{r}
g_change_percent <- c(0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      0,0,0,0,0,0,0,0,0,0,
                      
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      1,1,1,1,1,1,1,1,1,1,
                      
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      3,3,3,3,3,3,3,3,3,3,
                      
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      5,5,5,5,5,5,5,5,5,5,
                      
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      10,10,10,10,10,10,10,10,10,10,
                      
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      25,25,25,25,25,25,25,25,25,25,
                      
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50,
                      50,50,50,50,50,50,50,50,50,50
                      
                      )

g_change_percent



output_data <- as.data.frame(g_change_percent)

```


# Run models
```{r,eval=FALSE}
tryCatch(
for(i in seq_len(nrow(output_data))){

#generate data  
percent_change = g_change_percent[i]/100 
  
data <- simulate_catch_data(R =500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21 +(0.21*percent_change),
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.00) 


#create age and size bins
data <- create_bins(data,
                    bin_width_age = 1,
                    bin_width_size = 0.1)



###select subset of individuals for 'ageing' and apply linear model or ALK. Eg: simulating age/length(or weight) measurements made in lab from subset of individuals across all ages/sizes 

data <- age_data_with_literature_growth_rate(data = data)

#get sample size
output_data$sample_size[i] <- nrow(data)


#Sort ages into age bins, 1 day width
bin_width <- 1

cat_data <- lencat(~estimated_age, data = data, startcat = 0, w = bin_width, vname = "ageCat") ## uses agecat data, bins set at 1 day

## mode function for fully recruited age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


# Calculate the mode using the user function.
recruit_age <- getmode(cat_data$ageCat)
recruit_age

 
#Catch-curve method (Linear regression)
catch_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "lr") ##

output_data$catch_curve[i] <- as.numeric(catch_curve$`results`[3]) # extract z

#truncated catch-curve (weighted Linear regression)
trunc_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "wlr") ##

output_data$weighted_catch_curve[i] <- as.numeric(trunc_curve$`results`[3])# extract z



#Chapman-robson method
CRZ <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "crcb") 

output_data$Chapman_Robson[i] <- as.numeric(CRZ$`results`[3]) # extract z


#select data sample from stan known g model
data2 <- data_for_stan_size(data)

##sample from stan model
fit_size <- sampling(ret_size, data = data2, iter = 999, chains = 3)

output_data$stan_size[i] <- mean(rstan::extract(fit_size, pars="Z")[["Z"]])


}, error=function(e) e
)

saveRDS(output_data, "output/literature_growth_difference_with_true_g.rds")
```

# Read in output
```{r}
output_data <- readRDS("output/literature_growth_difference_with_true_g.rds")
```


# Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size")

output_data_long <- gather_(output_data, keycol, valuecol, gathercols)

head(output_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(output_data_long, aes(g_change_percent, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```



# Facet plot

Device size 6 x 13inch
```{r}

data <- output_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size")))
  
data

fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~g_change_percent, nrow = 1, ncol = 7) + labs(title = "% increase in literature g")#labs(title = expression('Variability around'~ bar(Z)))
 

fac_plot

lit_g_difference_g_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~g_change_percent, nrow = 1, ncol = 7) + labs(title = "% increase in literature g") #+  
  #theme(plot.title = element_textbox(hjust = 0.5, margin = margin(t = 5, b = 5)) #labs(title = expression('*Variability around*'~ bar(Z)))
 

lit_g_difference_g_fac_plot
```

# Extract data for summary table
## catch curve
```{r}
#catch curve
CC5 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 1) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 3) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 5) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 10) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 25) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- output_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 50) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```
## weighted catch curve
```{r}
#catch curve
wCC5 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 1) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 3) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 5) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 10) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 25) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- output_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 50) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 1) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 3) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 5) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 10) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 25) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- output_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 50) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan size
```{r}
#Stan size
SA5 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 0) %>%
  select(stan_size) 

mean(NaRV.omit(SA5$stan_size))
sd(NaRV.omit(SA5$stan_size))

#
SA10 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 1) %>%
  select(stan_size) 

mean(NaRV.omit(SA10$stan_size))
sd(NaRV.omit(SA10$stan_size))

#
SA20 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 3) %>%
  select(stan_size) 


mean(NaRV.omit(SA20$stan_size))
sd(NaRV.omit(SA20$stan_size))

#
SA50 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 5) %>%
  select(stan_size) 


mean(NaRV.omit(SA50$stan_size))
sd(NaRV.omit(SA50$stan_size))

#
SA100 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 10) %>%
  select(stan_size) 


mean(NaRV.omit(SA100$stan_size))
sd(NaRV.omit(SA100$stan_size))

#
SA500 <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 25) %>%
  select(stan_size) 


mean(NaRV.omit(SA500$stan_size))
sd(NaRV.omit(SA500$stan_size))

#
SA <- output_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 50) %>%
  select(stan_size) 


mean(NaRV.omit(SA$stan_size))
sd(NaRV.omit(SA$stan_size))

```


# Normalised results
## Normalise data around mean z 0.25

```{r}
normalised_data <- output_data

normalised_data$catch_curve <- ((normalised_data$catch_curve/0.25)*100)-100


normalised_data$weighted_catch_curve <- ((normalised_data$weighted_catch_curve/0.25)*100)-100


normalised_data$Chapman_Robson <- ((normalised_data$Chapman_Robson/0.25)*100)-100


normalised_data$stan_size <- ((normalised_data$stan_size/0.25)*100)-100

head(normalised_data)
```


# Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size")

normalised_data_long <- gather_(normalised_data, keycol, valuecol, gathercols)

head(normalised_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(normalised_data_long, aes(g_change_percent, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```



# Facet plot

Device size 6 x 13inch
```{r}

data <- normalised_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size")))
  
data

fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~g_change_percent, nrow = 1, ncol = 7) + labs(title = "% increase in literature g")#labs(title = expression('Variability around'~ bar(Z)))
 

fac_plot

normalised_lit_g_difference_g_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~g_change_percent, nrow = 1, ncol = 7) + labs(title = "% increase in literature g") #+  
  #theme(plot.title = element_textbox(hjust = 0.5, margin = margin(t = 5, b = 5)) #labs(title = expression('*Variability around*'~ bar(Z)))
 

normalised_lit_g_difference_g_fac_plot
```



# Extract normalised data for summary table
## catch curve
```{r}
#catch curve
CC5 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 1) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 3) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 5) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 10) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 25) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- normalised_data %>%
 select(g_change_percent, catch_curve) %>%
  filter(g_change_percent == 50) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```
## weighted catch curve
```{r}
#catch curve
wCC5 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 1) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 3) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 5) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 10) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 25) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- normalised_data %>%
 select(g_change_percent, weighted_catch_curve) %>%
  filter(g_change_percent == 50) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 1) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 3) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 5) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 10) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 25) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- normalised_data %>%
 select(g_change_percent, Chapman_Robson) %>%
  filter(g_change_percent == 50) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan size
```{r}
#Stan size
SA5 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 0) %>%
  select(stan_size) 

mean(NaRV.omit(SA5$stan_size))
sd(NaRV.omit(SA5$stan_size))

#
SA10 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 1) %>%
  select(stan_size) 

mean(NaRV.omit(SA10$stan_size))
sd(NaRV.omit(SA10$stan_size))

#
SA20 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 3) %>%
  select(stan_size) 


mean(NaRV.omit(SA20$stan_size))
sd(NaRV.omit(SA20$stan_size))

#
SA50 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 5) %>%
  select(stan_size) 


mean(NaRV.omit(SA50$stan_size))
sd(NaRV.omit(SA50$stan_size))

#
SA100 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 10) %>%
  select(stan_size) 


mean(NaRV.omit(SA100$stan_size))
sd(NaRV.omit(SA100$stan_size))

#
SA500 <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 25) %>%
  select(stan_size) 


mean(NaRV.omit(SA500$stan_size))
sd(NaRV.omit(SA500$stan_size))

#
SA <- normalised_data %>%
 select(g_change_percent, stan_size) %>%
  filter(g_change_percent == 50) %>%
  select(stan_size) 


mean(NaRV.omit(SA$stan_size))
sd(NaRV.omit(SA$stan_size))

```
