---
title: "Comparing the effect of Z variability on model efficacy when fish are aged with linear model"
author: "Charles Hinchliffe"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


The .rmd demonstartes the effect of variation in G on classic catch-curve methods, and our size-distribution model. To 'age' the data we use a linear model on a subset of the population simulated using simulate_catch_data(). 


# Load require packages and functions

```{r}
library(rstan)
library(tidyverse)
library(rstan)
library(dplyr)
library(ggplot2)
library(FSA)
library(fishmethods)
library(pracma)
library(bayesplot)
library(bayesboot)
library(see)
library(IDPmisc)

#agesurv funtion from 'fishmethods' with decimal rounding removed
source("R/agesurv_no_rounding.R")

#Data generation and manipulation functions
source("R/generate_sample.R")
source("R/trim_data_to_mode.R")
source("R/create_bins.R")

#For re-aging
source("R/age_data_with_linear_model.R")

#prapre data for stan model
source("R/data_for_stan_size_growth.R")
source("R/data_for_stan_size_growth_without_var.R")


#Plotting functions
source("R/plot_age_dist.R")
source("R/plot_size_dist.R")
source("R/element_textbox.R")
```



# Plot example simulated population
```{r}
#for plotting
pars <- list(R = 500,
             s0_av = 3,
             log10s0_sd = 0,
             g_av = 0.21,
             log10g_sd = 0,
             z_av = 0.25, 
             log10z_sd = 0.0,
             bin_width_age = 1,
             bin_width_size = 0.1)

pars2 <- list(R = 500,
             s0_av = 3,
             log10s0_sd = 0,
             g_av = 0.21,
             log10g_sd = 0.1,
             z_av = 0.25, 
             log10z_sd = 0.0,
             bin_width_age = 1,
             bin_width_size = 0.1)

#simulate populations
data <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.0)

data2 <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.1,
                            z_av = 0.25, 
                            log10z_sd = 0)


plot_size_dist(data,pars)


plot_size_dist(data2,pars2)

```


# Read in stan models
```{r, eval = FALSE}
#size distribution model and growth
ret_size_growth <- stan_model(file="stan/mortality_size_growth.stan")
```



# Select log10g_sd variability 


```{r}

variance <- c(0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              
              
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              
              
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              
              
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              
              
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              
              
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              
              
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1
              
              ) #700 0.1
              

output_data <- as.data.frame(variance)

growth_output <- as.data.frame(variance)

```


# Run models
```{r, eval = FALSE}
tryCatch(
for(i in seq_len(nrow(output_data))){

#generate data  
data <- simulate_catch_data(R = 500,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = variance[i],
                            z_av = 0.25, 
                            log10z_sd = 0.0) 


#create age and size bins
data <- create_bins(data,
                    bin_width_age = 1,
                    bin_width_size = 0.1)



###select subset of individuals for 'ageing' and apply linear model or ALK. Eg: simulating age/length(or weight) measurements made in lab from subset of individuals across all ages/sizes 

data <- age_data_with_linear_model(data = data, n_samples_each = 5)

growth_output$classic_models[i] <- mean(data$g_rate)

#get sample size
output_data$sample_size[i] <- nrow(data)


#Sort ages into age bins, 1 day width
bin_width <- 1

cat_data <- lencat(~estimated_age, data = data, startcat = 0, w = bin_width, vname = "ageCat") ## uses agecat data, bins set at 1 day

## mode function for fully recruited age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


# Calculate the mode using the user function.
recruit_age <- getmode(cat_data$ageCat)
recruit_age

 
#Catch-curve method (Linear regression)
catch_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "lr") ##

output_data$catch_curve[i] <- as.numeric(catch_curve$`results`[3]) # extract z

#truncated catch-curve (weighted Linear regression)
trunc_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "wlr") ##

output_data$weighted_catch_curve[i] <- as.numeric(trunc_curve$`results`[3])# extract z



#Chapman-robson method
CRZ <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "crcb") 

output_data$Chapman_Robson[i] <- as.numeric(CRZ$`results`[3]) # extract z


##Stan size dist growth model data
data2 <- data_for_stan_size_growth_without_var(data = data,
                                                  bin_width_size = 0.1,
                                                  rough_bin_width = 1.5,
                                                  n_samples_each = 5,
                                                  s0_av = 3)
##sample from stan model
fit_size_growth <- sampling(ret_size_growth, data = data2, iter = 999, chains = 3)
output_data$stan_size_growth[i] <- mean(rstan::extract(fit_size_growth, pars="Z")[["Z"]])

growth_output$stan_size_growth[i] <- mean(rstan::extract(fit_size_growth, pars="g")[["g"]])

}, error=function(e) e
)


saveRDS(output_data, "output/linear_model_ages_g.rds")

saveRDS(growth_output, "output/linear_model_ages_g_growthoutput.rds")
```

# Read in output
```{r}
output_data <- readRDS("output/linear_model_ages_g.rds")

growth_output <- readRDS("output/linear_model_ages_g_growthoutput.rds")
```



```{r}
head(output_data)
```

# Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size_growth")

output_data_long <- gather_(output_data, keycol, valuecol, gathercols)

head(output_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(output_data_long, aes(variance, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```
 
 
Plot var groups seperately  

```{r, eval = FALSE}
#Z_var = 0.00
var0 <- subset(output_data_long, variance == 0)

p5 <- ggplot(var0, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p5

##Z_var = 0.01
var0.01 <- subset(output_data_long, variance == 0.01)

p6 <- ggplot(var0.01, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0.01") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p6

#Z_var = 0.025
var0.02 <- subset(output_data_long, variance == 0.02)


p7 <- ggplot(var0.02, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0.02") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p7

#var = 0.03
var0.03 <- subset(output_data_long, variance == 0.03)


p8 <- ggplot(var0.03, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0.03") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p8

#var = 0.05
var0.05<- subset(output_data_long, variance == 0.05)


p9 <- ggplot(var0.05, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0.05") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p9
#var = 0.1
var0.1 <- subset(output_data_long, variance == 0.1)


p10 <- ggplot(var0.1, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10g_sd = 0.1") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p10
```



# Facet plot

```{r}

data <- output_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size_growth")))
  
data

fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "g variance")

fac_plot

linear_model_g_var_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "g variance")

linear_model_g_var_fac_plot
```



# Extract data for summary table
## catch curve
```{r}
#catch curve
CC5 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.005) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.01) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.02) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.03) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.05) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- output_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.1) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```

## weighted catch curve
```{r}
#catch curve
wCC5 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.005) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.01) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.02) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.03) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.05) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- output_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.1) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.005) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.01) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.02) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.03) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.05) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- output_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.1) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan size
```{r}
#Stan size
SA5 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA5$stan_size_growth))
sd(NaRV.omit(SA5$stan_size_growth))

#
SA10 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.005) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA10$stan_size_growth))
sd(NaRV.omit(SA10$stan_size_growth))

#
SA20 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.01) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA20$stan_size_growth))
sd(NaRV.omit(SA20$stan_size_growth))

#
SA50 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.02) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA50$stan_size_growth))
sd(NaRV.omit(SA50$stan_size_growth))

#
SA100 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.03) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA100$stan_size_growth))
sd(NaRV.omit(SA100$stan_size_growth))

#
SA500 <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.05) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA500$stan_size_growth))
sd(NaRV.omit(SA500$stan_size_growth))

#
SA <- output_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.1) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA$stan_size_growth))
sd(NaRV.omit(SA$stan_size_growth))

```


# Normalised results
## Normalise data around mean z 0.25

```{r}
normalised_data <- output_data

normalised_data$catch_curve <- ((normalised_data$catch_curve/0.25)*100)-100


normalised_data$weighted_catch_curve <- ((normalised_data$weighted_catch_curve/0.25)*100)-100


normalised_data$Chapman_Robson <- ((normalised_data$Chapman_Robson/0.25)*100)-100


normalised_data$stan_size_growth <- ((normalised_data$stan_size_growth/0.25)*100)-100

head(normalised_data)
```



## Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size_growth")

normal_data_long <- gather_(normalised_data, keycol, valuecol, gathercols)

head(normal_data_long)
tail(normal_data_long)
```


## Facet plot

Device size 6 x 13inch
```{r}

data <- normal_data_long %>% mutate(model = factor(model, levels=c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_size_growth")))
  
data


normal_linear_mod_g_var_fac_plot <- ggplot(data, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "g variance") #+  
  #theme(plot.title = element_textbox(hjust = 0.5, margin = margin(t = 5, b = 5)) #labs(title = expression('*Variability around*'~ bar(Z)))
 

normal_linear_mod_g_var_fac_plot
```


# Extract normalised data for summary table
## catch curve
```{r}
#catch curve
CC5 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0) %>%
  select(catch_curve) 

mean(NaRV.omit(CC5$catch_curve))
sd(NaRV.omit(CC5$catch_curve))

#
CC10 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.005) %>%
  select(catch_curve) 

mean(NaRV.omit(CC10$catch_curve))
sd(NaRV.omit(CC10$catch_curve))

#
CC20 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.01) %>%
  select(catch_curve) 


mean(NaRV.omit(CC20$catch_curve))
sd(NaRV.omit(CC20$catch_curve))

#
CC50 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.02) %>%
  select(catch_curve) 


mean(NaRV.omit(CC50$catch_curve))
sd(NaRV.omit(CC50$catch_curve))

#
CC100 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.03) %>%
  select(catch_curve) 


mean(NaRV.omit(CC100$catch_curve))
sd(NaRV.omit(CC100$catch_curve))

#
CC500 <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.05) %>%
  select(catch_curve) 


mean(NaRV.omit(CC500$catch_curve))
sd(NaRV.omit(CC500$catch_curve))

#
CC <- normalised_data %>%
 select(variance, catch_curve) %>%
  filter(variance == 0.1) %>%
  select(catch_curve) 


mean(NaRV.omit(CC$catch_curve))
sd(NaRV.omit(CC$catch_curve))
```
## weighted catch curve
```{r}
#catch curve
wCC5 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC5$weighted_catch_curve))
sd(NaRV.omit(wCC5$weighted_catch_curve))

#
wCC10 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.005) %>%
  select(weighted_catch_curve) 

mean(NaRV.omit(wCC10$weighted_catch_curve))
sd(NaRV.omit(wCC10$weighted_catch_curve))

#
wCC20 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.01) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC20$weighted_catch_curve))
sd(NaRV.omit(wCC20$weighted_catch_curve))

#
wCC50 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.02) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC50$weighted_catch_curve))
sd(NaRV.omit(wCC50$weighted_catch_curve))

#
wCC100 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.03) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC100$weighted_catch_curve))
sd(NaRV.omit(wCC100$weighted_catch_curve))

#
wCC500 <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.05) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC500$weighted_catch_curve))
sd(NaRV.omit(wCC500$weighted_catch_curve))

#
wCC <- normalised_data %>%
 select(variance, weighted_catch_curve) %>%
  filter(variance == 0.1) %>%
  select(weighted_catch_curve) 


mean(NaRV.omit(wCC$weighted_catch_curve))
sd(NaRV.omit(wCC$weighted_catch_curve))
```


## Chapman Robson
```{r}
#Chapman robson
CR5 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR5$Chapman_Robson))
sd(NaRV.omit(CR5$Chapman_Robson))

#
CR10 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.005) %>%
  select(Chapman_Robson) 

mean(NaRV.omit(CR10$Chapman_Robson))
sd(NaRV.omit(CR10$Chapman_Robson))

#
CR20 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.01) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR20$Chapman_Robson))
sd(NaRV.omit(CR20$Chapman_Robson))

#
CR50 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.02) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR50$Chapman_Robson))
sd(NaRV.omit(CR50$Chapman_Robson))

#
CR100 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.03) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR100$Chapman_Robson))
sd(NaRV.omit(CR100$Chapman_Robson))

#
CR500 <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.05) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR500$Chapman_Robson))
sd(NaRV.omit(CR500$Chapman_Robson))

#
CR <- normalised_data %>%
 select(variance, Chapman_Robson) %>%
  filter(variance == 0.1) %>%
  select(Chapman_Robson) 


mean(NaRV.omit(CR$Chapman_Robson))
sd(NaRV.omit(CR$Chapman_Robson))
```

## stan size
```{r}
#Chapman robson
SA5 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA5$stan_size_growth))
sd(NaRV.omit(SA5$stan_size_growth))

#
SA10 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.005) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA10$stan_size_growth))
sd(NaRV.omit(SA10$stan_size_growth))

#
SA20 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.01) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA20$stan_size_growth))
sd(NaRV.omit(SA20$stan_size_growth))

#
SA50 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.02) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA50$stan_size_growth))
sd(NaRV.omit(SA50$stan_size_growth))

#
SA100 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.03) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA100$stan_size_growth))
sd(NaRV.omit(SA100$stan_size_growth))

#
SA500 <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.05) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA500$stan_size_growth))
sd(NaRV.omit(SA500$stan_size_growth))

#
SA <- normalised_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.1) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA$stan_size_growth))
sd(NaRV.omit(SA$stan_size_growth))
```




# Facet plot for growth_output

Make long format data
```{r}
keycol <- "model"
valuecol <- "g"
gathercols <- c("classic_models", "stan_size_growth")

growth_output_long <- gather_(growth_output, keycol, valuecol, gathercols)

head(growth_output_long)
```

```{r}
normal_growth_fac_plot <- ggplot(growth_output_long, aes(x = model, y = g, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.21, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(g))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "g variance")
 

normal_growth_fac_plot
```



# Extract data for summary table g estimates
## catch curve
```{r}
#catch curve
CC5 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0) %>%
  select(classic_models) 

mean(NaRV.omit(CC5$classic_models))
sd(NaRV.omit(CC5$classic_models))

#
CC10 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.005) %>%
  select(classic_models) 

mean(NaRV.omit(CC10$classic_models))
sd(NaRV.omit(CC10$classic_models))

#
CC20 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.01) %>%
  select(classic_models) 


mean(NaRV.omit(CC20$classic_models))
sd(NaRV.omit(CC20$classic_models))

#
CC50 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.02) %>%
  select(classic_models) 


mean(NaRV.omit(CC50$classic_models))
sd(NaRV.omit(CC50$classic_models))

#
CC100 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.03) %>%
  select(classic_models) 


mean(NaRV.omit(CC100$classic_models))
sd(NaRV.omit(CC100$classic_models))

#
CC500 <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.05) %>%
  select(classic_models) 


mean(NaRV.omit(CC500$classic_models))
sd(NaRV.omit(CC500$classic_models))

#
CC <- growth_output %>%
 select(variance, classic_models) %>%
  filter(variance == 0.1) %>%
  select(classic_models) 


mean(NaRV.omit(CC$classic_models))
sd(NaRV.omit(CC$classic_models))
```


## stan size growth
```{r}
#Stan size
SA5 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA5$stan_size_growth))
sd(NaRV.omit(SA5$stan_size_growth))

#
SA10 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.005) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA10$stan_size_growth))
sd(NaRV.omit(SA10$stan_size_growth))

#
SA20 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.01) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA20$stan_size_growth))
sd(NaRV.omit(SA20$stan_size_growth))

#
SA50 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.02) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA50$stan_size_growth))
sd(NaRV.omit(SA50$stan_size_growth))

#
SA100 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.03) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA100$stan_size_growth))
sd(NaRV.omit(SA100$stan_size_growth))

#
SA500 <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.05) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA500$stan_size_growth))
sd(NaRV.omit(SA500$stan_size_growth))

#
SA <- growth_output %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.1) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA$stan_size_growth))
sd(NaRV.omit(SA$stan_size_growth))
```


# M/G

```{r}
variance <- output_data$variance

stan_g <- growth_output$stan_size_growth
classic_g <- growth_output$classic_models


catch_curveMG <- output_data$catch_curve/classic_g

weighted_catch_curveMG <- output_data$weighted_catch_curve/classic_g

Chapman_RobsonMG <- output_data$Chapman_Robson/classic_g

stanMG <- output_data$stan_size_growth/stan_g

mg_output <- cbind(variance,catch_curveMG, weighted_catch_curveMG, Chapman_RobsonMG, stanMG)

mg_output <- as.data.frame(mg_output)
```

Make long format data
```{r}
keycol <- "model"
valuecol <- "MG"
gathercols <- c("catch_curveMG", "weighted_catch_curveMG", "Chapman_RobsonMG", "stanMG")

mg_output_long <- gather_(mg_output, keycol, valuecol, gathercols)

head(mg_output_long)
```


```{r}
fac_plot <- ggplot(mg_output_long, aes(x = model, y = MG, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=1.190476, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right") +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(hat(M/G))) +
  facet_wrap(~variance, nrow = 1, ncol = 7)
 

fac_plot
```


# Normalised growth results
## Normalise growth data around mean g 0.21

```{r}
normalised_growth_data <- growth_output

normalised_growth_data$classic_models <- ((normalised_growth_data$classic_models/0.21)*100)-100


normalised_growth_data$stan_size_growth <- ((normalised_growth_data$stan_size_growth/0.21)*100)-100


head(normalised_growth_data)
```


## Facet plot for growth_output

Make long format data
```{r}
keycol <- "model"
valuecol <- "g"
gathercols <- c("classic_models", "stan_size_growth")

normal_growth_output_long <- gather_(normalised_growth_data, keycol, valuecol, gathercols)

head(normal_growth_output_long)
```

```{r}
normal_growth_fac_plot <- ggplot(normal_growth_output_long, aes(x = model, y = g, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "none", plot.title = element_textbox(color = "black", hjust = 0.5, margin = margin(t = 3, b = 3), face = "italic")) +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(bar(g))) +
  facet_wrap(~variance, nrow = 1, ncol = 7) + labs(title = "g variance")
 

normal_growth_fac_plot
```


# Extract normalised g estimates
## catch curve
```{r}
#catch curve
CC5 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0) %>%
  select(classic_models) 

mean(NaRV.omit(CC5$classic_models))
sd(NaRV.omit(CC5$classic_models))

#
CC10 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.005) %>%
  select(classic_models) 

mean(NaRV.omit(CC10$classic_models))
sd(NaRV.omit(CC10$classic_models))

#
CC20 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.01) %>%
  select(classic_models) 


mean(NaRV.omit(CC20$classic_models))
sd(NaRV.omit(CC20$classic_models))

#
CC50 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.02) %>%
  select(classic_models) 


mean(NaRV.omit(CC50$classic_models))
sd(NaRV.omit(CC50$classic_models))

#
CC100 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.03) %>%
  select(classic_models) 


mean(NaRV.omit(CC100$classic_models))
sd(NaRV.omit(CC100$classic_models))

#
CC500 <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.05) %>%
  select(classic_models) 


mean(NaRV.omit(CC500$classic_models))
sd(NaRV.omit(CC500$classic_models))

#
CC <- normalised_growth_data %>%
 select(variance, classic_models) %>%
  filter(variance == 0.1) %>%
  select(classic_models) 


mean(NaRV.omit(CC$classic_models))
sd(NaRV.omit(CC$classic_models))
```


## stan size growth
```{r}
#Stan size
SA5 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA5$stan_size_growth))
sd(NaRV.omit(SA5$stan_size_growth))

#
SA10 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.005) %>%
  select(stan_size_growth) 

mean(NaRV.omit(SA10$stan_size_growth))
sd(NaRV.omit(SA10$stan_size_growth))

#
SA20 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.01) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA20$stan_size_growth))
sd(NaRV.omit(SA20$stan_size_growth))

#
SA50 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.02) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA50$stan_size_growth))
sd(NaRV.omit(SA50$stan_size_growth))

#
SA100 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.03) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA100$stan_size_growth))
sd(NaRV.omit(SA100$stan_size_growth))

#
SA500 <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.05) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA500$stan_size_growth))
sd(NaRV.omit(SA500$stan_size_growth))

#
SA <- normalised_growth_data %>%
 select(variance, stan_size_growth) %>%
  filter(variance == 0.1) %>%
  select(stan_size_growth) 


mean(NaRV.omit(SA$stan_size_growth))
sd(NaRV.omit(SA$stan_size_growth))
```



# Normalised M/G

```{r}
normal_mg_output <- mg_output

normal_mg_output$catch_curveMG <- ((normal_mg_output$catch_curveMG/1.190476)*100)-100

normal_mg_output$weighted_catch_curveMG <- ((normal_mg_output$weighted_catch_curveMG/1.190476)*100)-100

normal_mg_output$Chapman_RobsonMG <- ((normal_mg_output$Chapman_RobsonMG/1.190476)*100)-100

normal_mg_output$stanMG <- ((normal_mg_output$stanMG/1.190476)*100)-100

head(normal_mg_output)
```

Make long format data
```{r}
keycol <- "model"
valuecol <- "MG"
gathercols <- c("catch_curveMG", "weighted_catch_curveMG", "Chapman_RobsonMG", "stanMG")

normal_mg_output_long <- gather_(normal_mg_output, keycol, valuecol, gathercols)

head(normal_mg_output_long)
```


```{r}
fac_plot <- ggplot(normal_mg_output_long, aes(x = model, y = MG, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right") +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(hat(M/G))) +
  facet_wrap(~variance, nrow = 1, ncol = 7)
 

fac_plot
```
