---
title: "Comparing the effect of s0 variability on model efficacy, when every fish has been aged"
author: "Charles Hinchliffe"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

The .rmd demonstartes the effect of variation in s0 on classic catch-curve methods, our continous catch-curve, and our R/Z age-distribution model. To 'age' the data we take the ages that are produced when a population is simulated using simulate_catch_data(). 


# Load require packages and functions

```{r}
library(rstan)
library(tidyverse)
library(rstan)
library(dplyr)
library(ggplot2)
library(see)
library(FSA)
library(fishmethods)
library(pracma)
library(bayesplot)
library(bayesboot)
library(see)

#agesurv funtion from 'fishmethods' with decimal rounding removed
source("R/agesurv_no_rounding.R")

#Data generation and manipulation functions
source("R/generate_sample.R")
source("R/trim_data_to_mode.R")
source("R/create_bins.R")

#For re-aging
source("R/real_aged_method.R")

#prapre data for stan model
source("R/data_for_stan_age.R")


#Plotting functions
source("R/plot_age_dist.R")
source("R/plot_size_dist.R")
```


# Example plots

Vary s0 and observe what happens to agr and size dist of population.
```{r}
#for plotting
pars <- list(R = 1000,
             s0_av = 3,
             log10s0_sd = 0,
             g_av = 0.21,
             log10g_sd = 0,
             z_av = 0.25, 
             log10z_sd = 0.0,
             bin_width_age = 1,
             bin_width_size = 0.1)

#simulate population
data <- simulate_catch_data(R = 1000,
                            s0_av = 3,
                            log10s0_sd = 0.0,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.0)

data2 <- simulate_catch_data(R = 1000,
                            s0_av = 3,
                            log10s0_sd = 0.05,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.00)

```

# Plot simulated population
```{r}
plot_age_dist(data,pars)
plot_age_dist(data2,pars)


#sizes
plot_size_dist(data,pars)
plot_size_dist(data2,pars)


```


# Read in stan models
```{r, eval = FALSE}
#age distribution model estimates R and Z
ret_age <- stan_model(file="stan/mortality_age.stan")

```


# Select S0_av variability 
```{r}
variance <- c(0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              0,0,0,0,0,0,0,0,0,0,
              
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,0.005,
              
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1
              )




output_data <- as.data.frame(variance)

```


# Run models 
```{r, eval = FALSE}
tryCatch(
for(i in seq_len(nrow(output_data))){

  
#generate data  
data <- simulate_catch_data(R = 1000,
                            s0_av = 3,
                            log10s0_sd = variance[i],
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0) 


#create age and size bins
data <- create_bins(data,
                    bin_width_age = 1,
                    bin_width_size = 0.1)


###select subset of individuals for 'ageing' and apply linear model or ALK. Eg: simulating age/length(or weight) measurements made in lab from subset of individuals across all ages/sizes 

data <- real_aged_data(data = data)

#get sample size
output_data$sample_size[i] <- nrow(data)


#Sort ages into age bins, 1 day width
bin_width <- 1


cat_data <- lencat(~estimated_age, data = data, startcat = 0, w = bin_width, vname = "ageCat") ## uses agecat data, bins set at 1 day

##re-adjust work-around for 0's
cat_data$ageCat <- (cat_data$ageCat-25)
data$estimated_age <- (data$estimated_age-25) 

## mode function for fully recruited age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


# Calculate the mode using the user function.
recruit_age <- getmode(cat_data$ageCat)
recruit_age 

min_est_age = min(cat_data$ageCat)
 
#Catch-curve method (Linear regression), use recruit_age to truncate, or min_est_age for all ages
catch_curve <- agesurv2(age=cat_data$ageCat, full = min_est_age, estimate = "z", method = "lr") ##

output_data$catch_curve[i] <- as.numeric(catch_curve$`results`[3]) # extract z

#truncated catch-curve (weighted Linear regression)
trunc_curve <- agesurv2(age=cat_data$ageCat, full = min_est_age, estimate = "z", method = "wlr") ##

output_data$weighted_catch_curve[i] <- as.numeric(trunc_curve$`results`[3])# extract z



#Chapman-robson method
CRZ <- agesurv2(age=cat_data$ageCat, full = min_est_age, estimate = "z", method = "crcb") 

output_data$Chapman_Robson[i] <- as.numeric(CRZ$`results`[3]) # extract z


#select data sample from stan known g model
data2 <- data_for_stan_age(data = data, bin_width_age = 1)

##sample from stan model
fit_age <- sampling(ret_age, data = data2, iter = 999, chains = 2)

output_data$stan_age[i] <- mean(rstan::extract(fit_age, pars="Z")[["Z"]])


}, error=function(e) e
)

saveRDS(output_data, "output/all_ages_s0.rds")
```

# Read in output

```{r}
output_data <- readRDS("output/all_ages_s0.rds")
```


```{r}
head(output_data)
```

# Plot output

Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")

output_data_long <- gather_(output_data, keycol, valuecol, gathercols)

head(output_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(output_data_long, aes(variance, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```




Plot var groups seperately  

variance <- c(0,0,0,0,0,0,0,0,0,0,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1)
```{r, eval = FALSE}
#Z_var = 0.00
var0 <- subset(output_data_long, variance == 0)

p5 <- ggplot(var0, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p5

##Z_var = 0.01
var0.01 <- subset(output_data_long, variance == 0.01)

p6 <- ggplot(var0.01, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.01") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p6

#Z_var = 0.025
var0.02 <- subset(output_data_long, variance == 0.02)


p7 <- ggplot(var0.02, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.02") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p7

#var = 0.03
var0.03 <- subset(output_data_long, variance == 0.03)


p8 <- ggplot(var0.03, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.03") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p8

#var = 0.05
var0.05<- subset(output_data_long, variance == 0.05)


p9 <- ggplot(var0.05, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.05") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p9
#var = 0.1
var0.1 <- subset(output_data_long, variance == 0.1)


p10 <- ggplot(var0.1, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.1") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p10
```


# Facet plot



Device size 6 x 13inch
```{r}
fac_plot2 <- ggplot(output_data_long, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right") +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(hat(Z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7)
 

fac_plot2
```




# Run models WITH trimming to mode
```{r, eval = FALSE}
tryCatch(
for(i in seq_len(nrow(output_data))){

  
#generate data  
data <- simulate_catch_data(R = 1000,
                            s0_av = 3,
                            log10s0_sd = variance[i],
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0) 


#create age and size bins
data <- create_bins(data,
                    bin_width_age = 1,
                    bin_width_size = 0.1)



###select subset of individuals for 'ageing' and apply linear model or ALK. Eg: simulating age/length(or weight) measurements made in lab from subset of individuals across all ages/sizes 

data <- age_data_with_literature_growth_rate(data = data)

#get sample size
output_data$sample_size[i] <- nrow(data)

#adjust estimated age to work around 0's
data$estimated_age <- (data$estimated_age+25) 


#Sort ages into age bins, 1 day width
bin_width <- 1


cat_data <- lencat(~estimated_age, data = data, startcat = 0, w = bin_width, vname = "ageCat") ## uses agecat data, bins set at 1 day

##re-adjust work-around for 0's
cat_data$ageCat <- (cat_data$ageCat-25)
data$estimated_age <- (data$estimated_age-25) 

## mode function for fully recruited age
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


# Calculate the mode using the user function.
recruit_age <- getmode(cat_data$ageCat)
recruit_age 

min_est_age = min(cat_data$ageCat)
 
#Catch-curve method (Linear regression), use recruit_age to truncate, or min_est_age for all ages
catch_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "lr") ##

output_data$catch_curve[i] <- as.numeric(catch_curve$`results`[3]) # extract z

#truncated catch-curve (weighted Linear regression)
trunc_curve <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "wlr") ##

output_data$weighted_catch_curve[i] <- as.numeric(trunc_curve$`results`[3])# extract z



#Chapman-robson method
CRZ <- agesurv2(age=cat_data$ageCat, full = recruit_age, estimate = "z", method = "crcb") 

output_data$Chapman_Robson[i] <- as.numeric(CRZ$`results`[3]) # extract z


#select data sample from stan known g model
data2 <- data_for_stan_size(data, trim_to_mode = TRUE)

##sample from stan model
fit_size <- sampling(ret_size, data = data2, iter = 999, chains = 2)

output_data$stan_age[i] <- mean(rstan::extract(fit_size, pars="Z")[["Z"]])


}, error=function(e) e
)

saveRDS(output_data, "output/all_ages_s0_with_trim.rds")
```

# Read in output WITH trim
```{r}
output_data <- readRDS("output/all_ages_s0_with_trim.rds")
```


# Plot output


Make long format data
```{r}
keycol <- "model"
valuecol <- "z"
gathercols <- c("catch_curve", "weighted_catch_curve", "Chapman_Robson", "stan_age")

output_data_long <- gather_(output_data, keycol, valuecol, gathercols)

head(output_data_long)
```

Plot long format trend line
```{r}
p4 <- ggplot(output_data_long, aes(variance, z, group = model, col = model)) +
  geom_point() +
  geom_smooth(method = "loess", se=F) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_classic()

p4
```




Plot var groups seperately  

variance <- c(0,0,0,0,0,0,0,0,0,0,
              0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,0.01,
              0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,0.02,
              0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,0.03,
              0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,0.05,
              0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1)
              
```{r, eval = FALSE}
#Z_var = 0.00
var0 <- subset(output_data_long, variance == 0)

p5 <- ggplot(var0, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p5

##Z_var = 0.01
var0.01 <- subset(output_data_long, variance == 0.01)

p6 <- ggplot(var0.01, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.01") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p6

#Z_var = 0.025
var0.02 <- subset(output_data_long, variance == 0.02)


p7 <- ggplot(var0.02, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.02") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p7

#var = 0.03
var0.03 <- subset(output_data_long, variance == 0.03)


p8 <- ggplot(var0.03, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.03") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p8

#var = 0.05
var0.05<- subset(output_data_long, variance == 0.05)


p9 <- ggplot(var0.05, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.05") +
  xlab("Model") + ylab("mean Z") # +
 # ylim(0,0.6)

p9
#var = 0.1
var0.1 <- subset(output_data_long, variance == 0.1)


p10 <- ggplot(var0.1, aes(x = model, y = z, fill = model, group = model)) +
  geom_violindot(size_dots = 5 ,fill_dots = "black", aes(x = model, y = z, fill = model, group = model), binwidth = 0.0005, trim = FALSE) +
  geom_hline(yintercept=0.25, linetype="dotdash", color = "black", size=1, alpha = 0.7) +
  theme_modern(axis.text.angle = 45) +
  scale_fill_material_d(palette = "ice") +
  ggtitle("log10s0_sd = 0.1") +
  xlab("Model") + ylab("mean Z") #+
  #ylim(0,0.6)

p10
```


# Facet plot

Device size 6 x 13inch
```{r}
fac_plot2 <- ggplot(output_data_long, aes(x = model, y = z, fill = model, group = model)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), trim = FALSE) +
  geom_hline(yintercept=0.25, color = "red", size=0.5, alpha = 0.5) +
  theme_bw() +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  theme(legend.position = "right") +
  scale_fill_material_d(palette = "ice") +
  ylab(expression(hat(Z))) +
  facet_wrap(~variance, nrow = 1, ncol = 7)
 

fac_plot2
```



