---
title: "Demo of trim_to_mode"
author: "Charles Hinchliffe"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

This notebook gives a demonstraiton of how the trim_to_mode function is used to return better estimates of $\hat{z}$ when there is variance in $s_0$ or 'net extrusion' applied when generating a population, such that max $n$ is not at $s=0$.

First, I show how this effects results from a 'literature aged scenario' using the stan_size_known_g, followed by the full stan_size_growth model. Note that variability in s0 has a greater effect on the first case. 

# Packages and functions
```{r}
library(tidyverse)
library(rstan)

#Data generation and manipulation functions
source("R/generate_sample.R")
source("R/trim_data_to_mode.R")
source("R/create_bins.R")

#prepare data for stan model
source("R/data_for_stan_size.R")
source("R/data_for_stan_size_growth_without_var.R")

#Plotting functions
source("R/plot_size_dist.R")
```


# Generate population with variance in individual s0.
```{r}
#simulate population
data <- simulate_catch_data(R = 1000,
                            s0_av = 3,
                            log10s0_sd = 0.03,
                            g_av = 0.21,
                            log10g_sd = 0.00,
                            z_av = 0.25, 
                            log10z_sd = 0.0)

data <- create_bins(data)
#for plotting
pars <- list(R = 1000,
             s0_av = 3,
             log10s0_sd = 0.05,
             g_av = 0.21,
             log10g_sd = 0,
             z_av = 0.25, 
             log10z_sd = 0,
             bin_width_age = 1,
             bin_width_size = 0.1)

plot_size_dist(data, pars)
```

# Read in stan models
```{r}
#size distribution model with known G
ret_size <- stan_model(file="stan/mortality_size_known_g.stan")

#size distribution model and growth model
ret_size_growth <- stan_model(file="stan/mortality_size_growth.stan")
```

# Size model with known G
Trim_to_mode = False
```{r}
##Prepare data for stan model
data_no_trim <- data_for_stan_size(data, trim_to_mode = FALSE)

##sample from stan model
fit_no_trim <- sampling(ret_size, data = data_no_trim, iter = 999, chains = 2)

print(fit_no_trim,  probs=c(0.025, 0.5, 0.975))
#stan_trace(fit_no_trim, pars = c("Z", "g", "R"), inc_warmup = TRUE)
```

With trim_to_mode = TRUE
```{r}
#select data sample from stan known g model
data_trimmed  <- data_for_stan_size(data, 
                            trim_to_mode = TRUE,
                            add_to_cut = 0)

##sample from stan model
fit_trimmed  <- sampling(ret_size, data = data_trimmed , iter = 999, chains = 2)

print(fit_trimmed,  probs=c(0.025, 0.5, 0.975))
#stan_trace(fit_trimmed, pars = c("Z", "g", "R"), inc_warmup = TRUE)
```


# Size and Growth model
Trim_to_mode = False
```{r}
##Prepare data for stan model
data_no_trim <- data_for_stan_size_growth_without_var(data = data, n_samples_each = 5)

##sample from stan model
fit_no_trim <- sampling(ret_size_growth, data = data_no_trim, iter = 999, chains = 2)

print(fit_no_trim,  probs=c(0.025, 0.5, 0.975))
#stan_trace(fit_no_trim, pars = c("Z", "g", "R"), inc_warmup = TRUE)
```

With trim_to_mode = TRUE
```{r}
data_trimmed <- data_for_stan_size_growth_without_var(data = data,
                                                  n_samples_each = 5,
                                                  trim_to_mode = TRUE,
                                                  add_to_cut = 0) #NB add_to_cut adjusts where the size class is trimmed

fit_trimmed <- sampling(ret_size_growth, data = data_trimmed, iter = 999, chains = 2)

print(fit_trimmed,  probs=c(0.025, 0.5, 0.975))
#stan_trace(fit_trimmed, pars = c("Z", "g", "R"), inc_warmup = TRUE)
```


